MSSM-Penn-Pitt - ACC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-05-04 individual-cohorts/MSSM-Penn-Pitt_ACC_FEATURECOUNTS_GRCh38_CQN.Rmd
fix knit2synapse

knit2synapse::createAndKnitToFolderEntity(file = "MSSM-Penn-Pitt_ACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                 parentId ="syn22012942",
                                 folderName = "MSSM-Penn-Pitt - ACC - DREAM - FEATURECOUNTS - GRCh38 - CQN")
```

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/MSSM-Penn-Pitt_ACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                 parentId ="syn22012942",
                                 folderName = "MSSM-Penn-Pitt - ACC - DREAM - FEATURECOUNTS - GRCh38 - CQN")
```
